Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models

### 2024-10-22 paper/paper.qmd
Abstract updated and format changed in appendix

---
title: "Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: https://github.com/zzq20010617/2024_USelection_prediction"
date: today
date-format: long
abstract: "1) what was done, 2) what was found, and 3) why this matters. 4) sentence."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

@@

# Idealized methodology

# Idealized Survey

# Trafalgar group’s methodology overview and evaluation

>>>>

---
title: "Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: https://github.com/zzq20010617/2024_USelection_prediction"
date: today
date-format: long
abstract: "This paper presents a multiple linear regression model for forecasting the outcome of the 2024 U.S. Presidential Election. Using nationwide polling data, we predict the percentage of support for U.S. presidential candidates based on key factors such as sample size, pollster quality, and timing. Our model aggregates these predictions to simulate potential election outcomes. The results reveal how specific poll attributes affect the accuracy of forecasts, offering valuable insights for predicting the likelihood of various electoral scenarios."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

@@

## Idealized  Survey and Methodology

## Trafalgar group’s methodology overview and evaluation
